\documentclass[format=sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

%opening
\title{Privacy in AI}
\author{Devin Trowbridge}
\affiliation{%
  \department{Computer Science and Software Engineering}
  \institution{Auburn University }
  \email{dkt0003@auburn.edu}
  \city{Huntsville}
  \state{Alabama}
  \country{United States}}

\begin{document}

\maketitle

\section{Can AI keep our lives private?}

Federal Computer Week published an article this week about ethics, compliance, and privacy in the realm of Artificial Intelligence \cite{fcw}. In the article, the author writes about the US Department of Defense Joint Artificial Intelligence Center's projects pertaining to health related data. The JAIC is past the realm of theoretical and into the realm of practice and application. Two projects, one that detects breast cancers cells in digital images and the other a response to COVID, are gathering and generating health data on individuals. Health data is considered exceptionally sensitive by most. So sensitive that in the United States enacted the HIPPA act of 1996 in order to protect healthcare information \cite{hippa}. The Association for Computing Machinery's Code of Ethics has a paragraph for respecting privacy which certainly applies here whether the developers at the JAIC were conscious of the Code of Ethics or not. Fortunately, ``The JAIC's ethics team has...launched a Responsible AI Champions pilot'' \cite{fcw} which aims to expand the role ethics plays in JAIC's organization. JAIC seems to understand ethics plays an important role in the work they do, so I believe they are acting in good faith and in accordance with the ACM Code of Ethics.

Several key points stick out as indicators of ethical behavior. The Department of Defense established principles of Artificial Intelligence Ethics in February \cite{dod}. The test, evaluation, and assessment lead said, ``Preserving personal health information is one of the JAIC's biggest priorities'' \cite{fcw}. Additionally, the DoD seems to be integrating ethics in at early stages in the development of their projects. For Project Salus, a COVID response project, JAIC, ``establish[ed] ethics and testing at the start mindset, especially as privacy became more important'' \cite{fcw}.
  
From this news article alone, the JAIC seems to be doing their ethical duty of protecting privacy as detailed by the ACM's Code of Ethics. The JAIC and DoD have created ethics guides, programs, and even ethics positions in their organization, and they seem to be incorporating ethics into their designs from an early stage of the design life-cycle. Therefore, the JAIC is acting ethically in accordance with the ACM Code of Ethics.

\medskip

\bibliographystyle{ACM-Reference-Format}
\bibliography{Module02}

\end{document}
